---
output: github_document
---
## `ib` - Isabella Benabaye's personal R package

### `ggplot2` functions

**`theme_ib`:** A simple `ggplot2` theme in my personal style. By default (`plots_pane = FALSE`), the theme adjusts the text sizes for printing images with width 10+ inches & height 8+ inches. `plots_pane = TRUE` is meant to be used when viewing plots in the plots pane and text sizes are not adjusted. There is also an option (`md = TRUE`) to use markdown theme elements from `ggtext` instead of `element_text()`. The fonts used are IBM Plex Sans & IBM Plex Mono, to load them you need `extrafont` and to run `extrafont::loadfonts(device = "win", quiet = TRUE)` if you're using Windows.

**`update_geom_fonts_ib`:** Update font defaults for text geoms to match `theme_ib`

**`scale_x_c_ib`:** Sets default values for the `expand` argument of `scale_x_continuous` that adds 0.5 units of space on both sides of the plot

**`scale_x_d_ib`:** Sets default values for the `expand` argument of `scale_x_discrete` that adds 0.5 units of space on both sides of the plot

**`scale_y_c_ib`:** Sets default values for the `expand` argument of `scale_y_continuous` such that there is no space below the lowest value and the top end of the plot is extended by 5% (eg. for use with bar plots)

**`scale_y_d_ib`:** Sets default values for the `expand` argument of `scale_y_discrete` such that there is no space below the lowest value and the top end of the plot is extended by 5% (eg. for use with bar plots)

### Exmaples
The following plots were taken from [Allison Horst](https://twitter.com/allison_horst)'s `palmerpenguins` [README](https://github.com/allisonhorst/palmerpenguins/blob/master/README.md).

Using `theme_ib` to print a scatter plot with width = 12 inches & height = 8 inches and the `md = TRUE` argument to use `ggtext::element_markdown()` instead of `element_text()` for text elements, in this case the subtitle:


```{r flipper_bill, fig.height=8, fig.width=12, message=FALSE, warning=FALSE}
library(ggplot2)
library(palmerpenguins)
library(ib)
extrafont::loadfonts(device = "win", quiet = TRUE) ## to load the font

ggplot(data = penguins,
       aes(x = flipper_length_mm,
           y = bill_length_mm)) +
  geom_point(aes(color = species),
             size = 3,
             alpha = 0.8, show.legend = FALSE) +
  geom_smooth(method = "lm", se = FALSE, aes(color = species), show.legend = FALSE) +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  labs(title = "Flipper and bill length",
       subtitle = "Dimensions for <span style = 'color:#FDA131;'>Adelie</span>, <span style = 'color:#B14AF1;'>Chinstrap</span> and <span style = 'color:#31A0A0;'>Gentoo Penguins</span> at Palmer Station LTER",
  x = "Flipper length (mm)",
y = "Bill length (mm)",
color = "Penguin species") +
  theme_ib(md = TRUE) +
  ggsave("flipper_bill.png",device = "png", type = "cairo", width = 12, height = 8, dpi = 300)
```

```{r flipper_hist, message=FALSE, warning=FALSE}
ggplot(data = penguins, aes(x = flipper_length_mm)) +
  geom_histogram(aes(fill = species),
                 alpha = 0.5,
                 position = "identity") +
  scale_fill_manual(values = c("darkorange","purple","cyan4")) +
  labs(title = "Penguin flipper lengths",
       x = "Flipper length (mm)",
       y = "Frequency",
       fill = "Penguin species") +
  theme_ib(plots_pane = TRUE) +
  scale_x_c_ib() +
  scale_y_c_ib()
```

